Developmental trajectories of bilingual word recognition

### 2023-11-27 manuscript/_appendix/_stimuli.qmd
Fix figure

>>>>

```{r tbl-stimuli}
#| label: tbl-stimuli
#| tbl-cap: "Summary of stimuli properties by trial type."
stimuli |>
	unnest_wider(c(freq, nphon)) |>
	summarise(across(c(matches("n_phon|freq_|lv_|nphon"), duration),
					 list(	mean = \(x) mean(x, na.rm = TRUE),
					 	  sd = \(x) sd(x, na.rm = TRUE))),
			  .by = c(trial_type, test_language)) |>
	select(-matches("distractor")) |>
	mutate(test_language = if_else(test_language=="English",
								   paste0("Study 1: ", test_language),
								   paste0("Study 2: ", test_language))) |>
	arrange(test_language) |> 
	gt(rowname_col = "trial_type",
	   groupname_col = "test_language") |>
	# summary_rows(groups = c("Unrelated", "Non-cognate", "Cognate"),
	# 			 columns = is.numeric,
	# 			 fns = list(Total ~ mean(.)),
	# 			 fmt = ~ fmt_number(., decimals = 2)) |>
	grand_summary_rows(	columns = is.numeric,
						fns = list(Total ~ mean(.)),
						fmt = ~ fmt_number(., decimals = 2)) |>
	tab_spanner("Phonemes", matches("nphon")) |>
	tab_spanner("Frequency (Zipf)", matches("freq")) |>
	tab_spanner("Phon. similarity [0-1]", matches("lv")) |>
	fmt_number(is.numeric, decimals = 1) |>
	cols_merge(c(freq_prime_mean, freq_prime_sd),
			   pattern = "{1} ({2})") |>
	cols_merge(c(freq_target_mean, freq_target_sd),
			   pattern = "{1} ({2})") |>
	cols_merge(c(nphon_prime_mean, nphon_prime_sd),
			   pattern = "{1} ({2})") |>
	cols_merge(c(nphon_target_mean, nphon_target_sd),
			   pattern = "{1} ({2})") |>
	cols_merge(c(lv_pp_mean, lv_pp_sd),
			   pattern = "{1} ({2})") |>
	cols_merge(c(lv_pt_mean, lv_pt_sd),
			   pattern = "{1} ({2})") |>
	cols_merge(c(duration_mean, duration_sd),
			   pattern = "{1} ({2})") |>
	cols_label(trial_type = "",
			   freq_prime_mean = "Prime",
			   freq_target_mean = "Target",
			   lv_pp_mean = "Prime-Prime",
			   lv_pt_mean = "Prime-Target",
			   duration_mean = "Duration (s)",
			   nphon_prime_mean = "Prime",
			   nphon_target_mean = "Target") |>
	tab_style(cell_text(style = "italic"),
			  list(cells_column_labels(),
			  	 cells_column_spanners(),
			  	 cells_grand_summary()))
```
